On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2018-08-29 docs/mvfits_paper/mvf.tex
Revert selected qualifier to select

To consider these two approaches in a largely automated way (i.e. where the set of possible basis functions is known, but the selected basis functions ultimately used are \textit{learned}), we will make use of the \textit{greedy} algorithm approach \cite{Field:2011mf}.

>>>>

To consider these two approaches in a largely automated way (i.e. where the set of possible basis functions is known, but the select basis functions ultimately used are \textit{learned}), we will make use of the \textit{greedy} algorithm approach \cite{Field:2011mf}.
